Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-05 docs/evol.tex
add material on bug persistence

\usepackage{url}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{threeparttable}

@@

>>>>

\usepackage{url}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{threeparttable}
\usepackage{pdflscape}
\usepackage{array}

@@

To examine the relation between the persistence of different kinds of
bugs, and of security bugs in particular, we used as a persistence
indicator the number of versions a bug remains open in a project. We
grouped the persistence numbers by bug categories and then performed
both descriptive statistics and a Mann-Whitney U test among all bug
category pairs. The results are presented in
Table~\ref{tbl:bug_persistence}. Cells in brackets show pairs where no
statistically significant difference was found.

In general, although the average number of versions bugs in different
bug categories remained opened was statistically different in many
cases, the difference is not spectacular. In all cases a bug persists
on average between two and three versions, with the difference being
in the decimal digits.

\begin{landscape}
  \begin{table}
    \centering
    \caption{Bug Persistence Comparison}
    \label{tbl:bug_persistence}
    \input{bug_persistence.tex}
  \end{table}
\end{landscape}
